WASP-4 is Accelerating Towards the Earth

### 2020-01-30 paper/ms.tex
add Howard Isaacson's suggestion

After identifying the period decrease in
\citetalias{bouma_wasp4b_2019}, we acquired four additional radial
velocity measurements with the Keck High Resolution Echelle
Spectrometer (HIRES; \citealt{vogt_hires_1994}).  Our observations
were acquired under the purview of the California Planet Survey
\citep{howard_cps_2010}.  The spectra were reduced using {\bf software
X}.  Previously, the HIRES data-points spanned 2010 to 2013
\citep{knutson_friends_2014}.  Our new measurements triple the HIRES
observing baseline to nine years.

>>>>

After identifying the period decrease in
\citetalias{bouma_wasp4b_2019}, we acquired four additional radial
velocity measurements with the Keck High Resolution Echelle
Spectrometer (HIRES; \citealt{vogt_hires_1994}).  Our observations
were acquired using the standard setup and reduction techniques of the
California Planet Survey \citep{howard_cps_2010}.  Previously, the
HIRES data-points spanned 2010 to 2013 \citep{knutson_friends_2014}.
Our new measurements triple the HIRES observing baseline to nine
years.
